MCR_Algae_Data_Cleaning

### 2024-11-20 Personal_Prelim_Code/mcr_algal_data_cleaning_final.Rmd
Added taxa information for folks to see but changed Caulerpa racemosa back so Naom can decide

>>>>

# Julianna notes on taxa:
# Changed Caulerpa peltata to Caulerpa chemnitzia 
# Changed Chnoospora implexa to Pseudochnoospora implexa
# Changed Neogoniolithon frutescens to Neogoniolithon brassica-florida
# Changed Caulerpa pickeringii to Caulerpa webbiana
# Changed Boodlea kaeneana to Cladophoropsis membranacea
# Changed Dictyota divaricata to Dictyota cervicornis
